# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r cache = TRUE}
untar("./activity.zip", compressed = 'gzip')
datas <- read.csv('./activity.csv', na.strings="NA")
```
We now have to convert the "date" field to a proper 'Date' datatype
```{r cache = TRUE}
datas[, "date"] <- as.Date(datas$date)
```

### removing NAs value for steps and transform date column to date value 
```{r}
datas_nona <- datas[!is.na(datas$steps),]

```

## What is mean total number of steps taken per day?
We use here the package PLYR, which is a tool for doing split-apply-combine procedures in a way that resambes the *SQL* command *GROUP BY*
```{r}
library(plyr)
daily_steps <- ddply(datas_nona, .(date), summarise, steps=sum(steps))
```
Or we can use the function *aggregate*
```{r}
freqs <- aggregate(datas_nona$steps, by=list(datas_nona$date), FUN=sum)
```
Simple histogram and mean and median
```{r}
hist(daily_steps$steps, xlab="steps per day")
mean(daily_steps$steps)
median(daily_steps$steps)
```

## What is the average daily activity pattern?

```{r}
average_date <- ddply(datas_nona, .(interval), summarise, steps=mean(steps))
plot(average_date$interval, average_date$steps, type="l", xlab="5-minute interval", 
ylab="Average steps",main="Average daily activity")

# Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
average_date[average_date$steps==max(average_date$steps),]
```



## Imputing missing values
```{r}
colnames(average_date)[2] <- "intervalAvg"
head(average_date)
merged <- join(datas, average_date)
names(merged)
head(merged)

merged$steps[is.na(merged$steps)] <- merged$intervalAvg[is.na(merged$steps)]
new_daily_steps <- ddply(merged, .(date), summarise, steps=sum(steps))
hist(new_daily_steps$steps, main="Number of Steps", xlab="steps taken each day",,)
```


```{r}
mean(new_daily_steps$steps)
median(new_daily_steps$steps)
daily_steps_1 <- sum(datas_nona$steps)
daily_steps_2 <- sum(merged$steps)
diff <- daily_steps_2 -daily_steps_1 []
```
Mean values didn't change as imputation used the average on 5-mi interval

## Are there differences in activity patterns between weekdays and weekends?
```{r}
weekdays <- weekdays(as.Date(merged$date))
data_weekdays <- cbind(merged, day = weekdays)
data_weekdays$wk <- ifelse(data_weekdays$day %in% c("Saturday", "Sunday"),"weekend", "weekday")
average_week <- ddply(data_weekdays, .(interval, wk), summarise, steps=mean(steps))
library(lattice)

xyplot(steps ~ interval | wk, data = average_week, layout = c(1, 2), type="l")
```
