# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r cache = TRUE}
untar("./activity.zip", compressed = 'gzip')name
datas <- read.csv('./activity.csv', na.strings="NA")
```
We now have to convert the "date" field to a proper 'Date' datatype
```{r cache = TRUE}
datas[, "date"] <- as.Date(datas$date)
```

### removing NAs value for steps and transform date column to date value 
```{r}
datas_nona <- datas[!is.na(datas$steps),]

```

## What is mean total number of steps taken per day?
We use here the package PLYR, which is a tool for doing split-apply-combine procedures in a way that resambes the *SQL* command *GROUP BY*
```{r}

daily_steps <- ddply(datas_nona, .(date), summarise, steps=sum(steps))
```
Or we can use the function *aggregate*
```{r}
freqs <- aggregate(datas_nona$steps, by=list(datas_nona$date), FUN=sum)
```
Simple histogram and mean and median
```{r}
hist(daily_steps$steps, xlab="steps per day")
mean(daily_steps$steps)
median(daily_steps$steps)
```

## What is the average daily activity pattern?

```{r}
average_date <- ddply(datas_nona, .(interval), summarise, steps=mean(steps))
plot(average_date$interval, average_date$steps, type="l", xlab="5-minute interval", 
ylab="Average steps",main="Average daily activity")

# Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
average_date[average_date$steps==max(average_date$steps),]
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
